Approximation as Differentiation notes

### 2025-02-25 notes/sec/grothendieck.tex
We need that Fam(-) preserves products.

@@

\begin{proof}
Define $[(I, X), (J, Y)]$ to be the hom-object $(K,Z)$ in $\Fam(C)$ where $K$ is the set of morphisms from
$\Fam(I,C)$ to $\Fam(J,C)$ and $Z$ is the $K$-indexed family in $\Fam(K,C)$ which maps every $f: \Fam(I,C) \to
\Fam(J,C)$ in $K$ to $\prod_{i \in I}\reindex{Y}{f}_i$. Then the following families of morphisms in $\Fam(C)$:
\begin{enumerate}
\item $\lambda_{(I,X),(J,Y),(K,Z)}: \Fam(C)((I,X) \tensor (J,Y), (K,Z)) \to \Fam(C)((I,X), [(J,Y), (K, Z)])$
\item $\eval_{(I,X),(J,Y)}: [(I, X), (J, Y)] \tensor (I, X) \to (J, Y)$
\end{enumerate}
\end{proof}

>>>>

\begin{proposition}
If $C$ has products then $\Fam(C)$ has products.
\end{proposition}

@@

\begin{proof}
Suppose $X = (I, X)$ and $Y = (I, Y)$ are objects in $\Fam(C)$. Define $[X, Y]$ to be the object $(K,Z)$ in
$\Fam(C)$ where $K$ is the set of morphisms from $\Fam(I,C)$ to $\Fam(J,C)$ and $Z$ is the $K$-indexed family
which maps every $f: \Fam(I,C) \to \Fam(J,C)$ in $K$ to $\prod_{i \in I}\reindex{Y}{f}_i$. Then the following
families of morphisms in $\Fam(C)$:
\begin{enumerate}
\item $\lambda_{X,Y,Z}: \Fam(C)(X \times Y, Z) \to \Fam(C)(X, [Y, Z])$
\item $\eval_{X,Y}: [X, Y] \times X \to Y$
\end{enumerate}
\end{proof}
